### 2021-04-30 article/article.tex

\documentclass[draft=True]{revtex4-2}
\newcommand{\zreco}{\ensuremath{\cos{(\theta_z^{reco})}}}
\newcommand{\ztrue}{\ensuremath{\cos{(\theta_z^{true})}}}
\newcommand{\emm}{\ensuremath{\epsilon_{\mu\mu}}}
\newcommand{\emt}{\ensuremath{\epsilon_{\mu\tau}}}
\newcommand{\eet}{\epsilon_{e\tau}}
\newcommand{\eem}{\epsilon_{e\mu}}
\newcommand{\ett}{\ensuremath{\epsilon_{\tau\tau}}}
\newcommand{\ep}{\ensuremath{\epsilon^\prime}}
\renewcommand{\ne}{\nu_e}
\newcommand{\nm}{\nu_\mu}
\newcommand{\nt}{\nu_\tau}
\newcommand{\ane}{\bar\nu_e}
\newcommand{\anm}{\bar\nu_\mu}
\newcommand{\ant}{\bar\nu_\tau}
\newcommand{\dm}{\Delta m^2_{31}}
\newcommand{\sth}{\sin^2(2\theta_{23})}

@@

\subsection{IceCube}\label{ch:ICmethod}
The event rate for each bin reads
\begin{align}\label{eq:ICevents}
    N_{ij} &= T \int_{(\cos{\theta_z^r})_i}^{(\cos{\theta_z^r})_{i+1}} \dd \cos{\theta^r_z} \int_{E^r_{j}}^{E^r_{j+1}} \dd E^r \int_0^\pi R(\theta^r,\theta^t) \dd \cos{\theta^t} \int_0^\infty R(E^r,E^t) \dd E^t
    \times \left[ \sum_\beta \phi_\beta^\text{det}  A^\text{eff}_\beta\right]\,,
\end{align}
where $T$ is the live time of the detector, and $A^\text{eff}_\beta$ its effective area for flavor $\beta$. We use the effective area of the 86 string configuration made public by the IceCube collaboration~\cite{ICaeff}. $R(x^r,x^t)$ is a resolution function, 
which is responsible for the smearing between the reconstructed and true parameters $x^r$ and $x^t$, respectively. We assume a log-normal distribution, giving it the form 
\begin{align}
    R(x^r, x^t) = \frac{1}{\sqrt{2\pi} \sigma_{x^r}x^r} \exp\left[-\frac{(\log x^r-\mu(x^t))^2}{2\sigma_{x^r}^2}\right]\,.
\end{align}
As seen in Fig.~\ref{fig:IC_MC_counts}, the energy reconstruction is biased. To model this relationship between $E^{true}$ and $E^{reco}$, we train a Gaussian process regressor on the dataset~\cite{IC2016}, from which
we can extract a predicted mean and standard deviation for a given $E^{reco}$. We then take the $E^\text{true}$ points of the 99th percentile of each distribution to obtain
the limits of $E^\text{true}$ at which to integrate over. We have no angular resolution function since the angle resolution in Icecube for track-like events is less than $\SI{2}{\degree}$, making $\ztrue$ coincide with $\zreco$ for our study~\cite{IC2020}. 
The data is from the IC86 sterile analysis~\cite{IC2020}.
\begin{figure}[!tb]
    \begin{center}
       \includegraphics[width=0.4\linewidth]{figures/IC_MC_gpr.pdf} %TODO: another fig here? Aeff?
    \end{center}
    \caption{Relationship between the true and reconstructed muon energy in the IceCube MC sample~\cite{IC2016}}\label{fig:IC_MC_counts}. Shaded area shows the $99.9$th percentile limits predicted by the regressor trained on this set.
 \end{figure}

>>>>

\documentclass[draft=True]{revtex4-2}
\newcommand{\zreco}{\ensuremath{\cos{(\theta_z^{reco})}}}
\newcommand{\ztrue}{\ensuremath{\cos{(\theta_z^{true})}}}
\newcommand{\emm}{\ensuremath{\epsilon_{\mu\mu}}}
\newcommand{\emt}{\ensuremath{\epsilon_{\mu\tau}}}
\newcommand{\eet}{\epsilon_{e\tau}}
\newcommand{\eem}{\epsilon_{e\mu}}
\newcommand{\ett}{\ensuremath{\epsilon_{\tau\tau}}}
\newcommand{\ep}{\ensuremath{\epsilon^\prime}}
\renewcommand{\ne}{\nu_e}
\newcommand{\Ereco}{E^{reco}}
\newcommand{\Etrue}{E^{true}}
\newcommand{\nm}{\nu_\mu}
\newcommand{\nt}{\nu_\tau}
\newcommand{\ane}{\bar\nu_e}
\newcommand{\anm}{\bar\nu_\mu}
\newcommand{\ant}{\bar\nu_\tau}
\newcommand{\dm}{\Delta m^2_{31}}
\newcommand{\sth}{\sin^2(2\theta_{23})}

@@

\subsection{IceCube}\label{ch:ICmethod}
The event rate for each bin reads
\begin{align}\label{eq:ICevents}
    N_{ij} &= T \int_{(\cos{\theta_z^r})_i}^{(\cos{\theta_z^r})_{i+1}} \dd \cos{\theta^r_z} \int_{E^r_{j}}^{E^r_{j+1}} \dd E^r \int_0^\pi R(\theta^r,\theta^t) \dd \cos{\theta^t} \int_0^\infty R(E^r,E^t) \dd E^t
    \times \left[ \sum_\beta \phi_\beta^\text{det}  A^\text{eff}_\beta\right]\,,
\end{align}
where $T$ is the live time of the detector, and $A^\text{eff}_\beta$ its effective area for flavor $\beta$. We use the effective area of the 86 string configuration made public by the IceCube collaboration~\cite{ICaeff}. $R(x^r,x^t)$ is a resolution function, 
which is responsible for the smearing between the reconstructed and true parameters $x^r$ and $x^t$, respectively. We assume a log-normal distribution, giving it the form 
\begin{align}
    R(x^r, x^t) = \frac{1}{\sqrt{2\pi} \sigma_{x^r}x^r} \exp\left[-\frac{(\log x^r-\mu(x^t))^2}{2\sigma_{x^r}^2}\right]\,.
\end{align}
As seen in Fig.~\ref{fig:IC_MC_counts}, the energy reconstruction is biased. To model this relationship between $\Etrue$ and $\Ereco$, we train a Gaussian process regressor on the dataset~\cite{IC2016}, from which
we can extract a predicted mean and standard deviation for a given $E^{reco}$. We then take the $\Etrue$ points of the 99th percentile of each distribution to obtain
the limits of $\Etrue$ at which to integrate over. We have no angular resolution function since the angle resolution in Icecube for track-like events is less than $\SI{2}{\degree}$, making $\ztrue$ coincide with $\zreco$ for our study~\cite{IC2020}. 
The data is from the IC86 sterile analysis~\cite{IC2020}.
\begin{figure}[!tb]
    \begin{center}
       \includegraphics[width=0.4\linewidth]{figures/IC_MC_gpr.pdf} %TODO: another fig here? Aeff?
    \end{center}
    \caption{Relationship between the true and reconstructed muon energy in the IceCube MC sample~\cite{IC2016}}\label{fig:IC_MC_counts}. Shaded area shows the $99.9$th percentile limits predicted by the regressor trained on this set.
 \end{figure}
